\documentclass{article}
    % General document formatting
    \usepackage[margin=0.7in]{geometry}
    \usepackage[parfill]{parskip}
    \usepackage[utf8]{inputenc}
    
    % Related to math
    \usepackage{amsmath,amssymb,amsfonts,amsthm}

\begin{document}

\title{Declaration of consent for cohabitation}
\date{}
\maketitle

To whom it may concern,

\vspace{5pt}

I, Haoyang Ye, resident of Leiden 2334 EK Boerhaavelaan 223, Netherlands,
holder of Dutch Residency Permit No. VKBR31F57 and Dutch Citizen Service No.
6698.18.823.

Do solemnly and sincerely DECLARE and say as follows:

\begin{enumerate}
\item I am the owner of the property at address Leiden 2334 EK Boerhaavelaan 223, Netherlands.
\item I am resident at address Leiden 2334 EK Boerhaavelaan 223, Netherlands, and my residency is registered at the time of writing with the Municipality of Leiden.
\item I consent to William Edward Vandepeer Barker, born on 27\textsuperscript{th} January 1995 and currently aged 27, formerly of Leiden 2333 BW Dankmeijerpad 90, Netherlands, holder of Dutch Residency Permit No. VYKJB4753 and Brititsh Passport No. 514407773 and Dutch Citizen Service No. 5374.50.932, to live with me at Leiden 2334 EK Boerhaavelaan 223, Netherlands, commencing on 15\textsuperscript{th} May 2022 and remaining in effect indefinitely.
\end{enumerate}

I make this declaration conscientiously believing the same to be true.

\vspace{20pt}

Signed:\ \ ........................................

Printed name: HAOYANG YE

Date:\ \ ........................................

\end{document}
